\documentclass[]{article}
\begin{document}
\textbf{\huge{LV8} Erik Waser}

\begin{itemize}
    \item \textbf{What do I want to learn or understand better?} \newline
    I don't think this will apply to the coming week. Next week is more about writing down what we have learned and thought about. I suppose it will be nice to hear abot the others' thoughts about our process and the course as a whole. However i think we have been pretty open about what we have thought throughout the course os I don't think we will be having a lot of surprising thouhts. 
    
    \item \textbf{How can I help someone else, or the entire team, to learn something new?} \newline
    For the coming week I am one of the few of us that haven't got exams during next week. Because of this we have made our schedule for writing the final reflection around the people who have got exams and I will be taking an extra role in making sure that what we discuss and reflect on gets written down in a representative way. 
    
    
    \item \textbf{What is my contribution towards the team’s use of Scrum?} \newline
    This week has been a lot of preparing for the presentation, in that preperation we collectively had a couple of planning meetings. 
    
    

    
    \item \textbf{What is my contribution towards the team’s deliveries?} \newline
    I helped in the presentation. Mostly in my contribution of writing a big part of the rough "script" we used. The plan was for me to talk about what we had learned during the course but when presenting our project we omitted that part in favour of answering questions more related to the project itself. 
    
    
    
\end{itemize}

\end{document}

