\documentclass{scrartcl}

\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0em}

\usepackage{polyglossia,graphicx}
\setdefaultlanguage{english}
\usepackage{csquotes}


\begin{document}

\title{Gruppreflektion för vecka 8}
\author{Group Joy}
\date{24 oktober 2021}
\maketitle

\section{Customer Value and Scope}
The scope we decided for this weeks development was to have a finished product. Meaning, the map would change as a ratio, rather than solid number, the legend should be included and working, and the map would update depending on which age group that was chosen. This was also our criteria for success. Acceptance criteria this week were close to none, since we really stressed in implementing the final parts of our project ahead of the presentation, and felt we would rather show the final product working, and clean up the code afterwards. We feel that this isn't optimal, however neccesary with our time being limited. Some also have exams on saturday, and with them wanting to focus on that, we've decided will sit down together and finish the project structure and perform final tests on sunday.

\section{Social Contract and Effort}
This week we've been working quite hard since we wanted to finish our project on time ahead of the project presentation. We've worked both on how we would present our project, as well as finalizing the actual product. We ended up not finishing it on time, but soon after the presentation the product was finalized, which felt really rewarding. We would summarize it as a good time to delivery rate.

\section{Design decisions and product structure}
So far we have'nt made any documentation on the code. This could be useful to implement, especially for a better understanding of how the code extracts and uses data, and should be looked in to. \newline
This week Erik has been responsible for updating the code and adjust so that every piece of code folows our coding standard. This was made easy by the script included by Albin that checks each file for inconcistencies. The code now follows a more uniform look and is easier to read. 

\section{Application of Scrum}
Overall, the application of Scrum has been weak this sprint. A lot of focus has fallen on the presentation, as well as preparing for the final hand-in. Perhaps we could implement scrum for the final hand-in to ease who-does-what in terms of the reflection, as well as finishing our repository.

\end{document}
